---
title: "tabfig"
author: "Bryce Bartlett"
date: "December 21, 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, cache=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = 'H:/prjects/happy_gene/code')
#source('H:/projects/happy_gene/code/funs.R')
source("H:/projects/happy_gene/code/config~.R")
load('H:/projects/happy_gene/analyze_env~.RData')

```

Table 1 full descriptives.

```{r descriptive, echo=FALSE}


v=c('cesd','md_cesd','fd_cesd','ret','unemp','age',
    'pm_uer','md_uer','fd_uer',
    'lnwlth','negwlth','lninc','male','marr')

d = as.data.frame(do.call(cbind,lapply(split(analyze,factor(analyze$period)),
           function(x) descriptives(df=x,vars=v)[,1:2])))

#test differnece in means over periods
delt = sig(bi.test(df=analyze,vars=v,slice='period')[,'pval'])

d$pval = unlist(delt)

ids = analyze %>% 
  group_by(period) %>% 
  summarize(n=n(),
              i=length(unique(hhidpn)))

kable(cbind(d,descriptives(df=analyze,vars=v)[,3:5]),
      digits=3,
      caption=ids)


```

## Individual level descriptives


```{r idescribe, echo=FALSE}

nw = analyze %>%
  group_by(rahhidpn) %>% 
  summarize(male = mean(male,na.rm=TRUE),
            nwave = n(),
            icesd = mean(cesd,na.rm=TRUE),
            pgs.swb = mean(pgs.swb,na.rm=TRUE),
            iuer = mean(pm_uer,na.rm=TRUE),
            ret = mean(ret,na.rm=TRUE),
            unemp = mean(unemp,na.rm=TRUE),
            dead = mean(!is.na(randate))) %>%
  ungroup

sel = colnames(nw)[colnames(nw)!='rahhidpn']

res = descriptives(df=nw,
                   vars=sel)

kable(res,caption=paste0('n=',nrow(nw)))

```

Figure 1. PGS Quintiles and ICESD.

```{r imeans,echo=FALSE}
print(imeans)
```



Figure 2. Unemployment Rate over time.

```{r uetrend, echo=FALSE}
print(uetrend)

```


Figure 3. CESD and Unemployment Rate by PGS Quintile

```{r deltaviz, echo=FALSE}
print(deltaviz)

```


Table __. Results of environment and interaction models.

```{r initial effects}

ee = mktab(plm.e); ee$eff=row.names(ee)
be = mktab(plm.gxe); be$eff = row.names(be)

bm = data.frame(eff=ee$eff)
bm = merge(bm,ee,all=TRUE)
kable(merge(bm,be,by='eff',all=TRUE))

```



Table __. Results of Cross-year interaction models.

```{r model results, echo=FALSE}

plm.split

```


Results figure.

```{r envfig, echo=FALSE}

print(FE.gxenv2)

```


## Some supplemental stuff.

Additional Descriptive plots: Distribution of changes (first difference).



```{r}
ggplot(analyze,aes(fd_uer)) + 
  geom_histogram(bins=50) + 
  facet_grid(pgs.quart5~period) + 
  geom_vline(xintercept=c(-1,0,1)) + 
  theme_minimal()

```


First difference model (because the u/e rate is dependent on the last level, i.e. not random).

```{r}
fd.gxe <- plm(cesd ~ pm_uer*(ret + unemp)+
                (pm_uer*(ret + unemp)):pgs.swb, data=analyze, 
              index=c("hhidpn", "iwendy"), 
              na.action=na.omit, model="fd")
mktab(fd.gxe)
```

```{r}
fd.gxe2 <- lapply(split(analyze,analyze[,'period']), function(x)
  plm(cesd ~ pm_uer + pm_uer:pgs.swb, data=x, 
              index=c("hhidpn", "iwendy"), 
              na.action=na.omit, model="fd"))

lapply(fd.gxe2,mktab)


```

## Pooled dummy first difference model

Note that results below display the same associtions with a reduced model; using a first-difference model eliminates 10,000 observations and statistical significance.

```{r}
fd.gxe <- plm(cesd ~ (pm_uer + pm_uer:pgs.swb + lnwlth + lninc + negwlth + marr + unemp + ret)*period, data=analyze, 
              index=c("hhidpn",'iwendy'), 
              na.action=na.omit, model="fd")
mktab(fd.gxe)
```

## "Hybrid" Random Effects model.

```{r}

hlm.gxe1 = lmer(cesd~(iuer + md_uer + recession)*pgs.swb +
                 male  + raedyrs + age +
                 marr + lninc_i + lnwlth_i + negwlth_i +
                 lninc_md + lnwlth_md + negwlth_md +
                 (md_unemp + md_ret + iunemp + iret)*pgs.swb +
                 (1|hhidpn),
               data=analyze)

mktab(hlm.gxe1)

```


## Factor based analysis with plm.

```{r}


mktab(
  plm(cesd~age + (ret + unemp)*pm_uer + marr + iwendy +
                (ret+unemp)*pm_uer + lninc+lnwlth+negwlth +
                (pm_uer + (ret+unemp)*pm_uer):pgs.quart5,
           index='hhidpn',model='within',data=analyze)
)
```



Evidence of increasing uncertainty in retirement.

```{r retirement1, echo=FALSE}

ggplot(cleandat,aes(x=iwendy,y=age+rplnya-iwendy)) +
  geom_smooth() +
  geom_smooth(aes(y=age+rplnyr-iwendy),lty=2) +
  theme_classic() + geom_abline(slope=0,intercept=65) +
  labs(title='Smoothed retirement plans (dashed) and expectations (solid).',
       caption='Full non-retired sample.')
  

```

```{r}
ggplot(cleandat,aes(x=iwendy,y=work65,
                    color=factor(ret),group=factor(ret))) +
  geom_smooth() +
  geom_smooth(aes(y=work62),lty=2) +
  theme_classic() + geom_abline(slope=0,intercept=65) +
  labs(title='Subjective probability for working past 62 (dashed) and 65.',
       caption='Full sample.')
```

```{r}

analyze = analyze %>% 
  mutate(rage = rplnya - iwendy + age)

summary(
  plm(cesd~age + pm_uer + marr + iwendy + 
                 lninc+lnwlth+negwlth + rage + 
                pm_uer:pgs.quart,
           index='hhidpn',model='within',
      data=analyze )
)

```

No appreciable differneces in survival (by quartile)

```{r}
print(survplot)
```

